Deciding Bitvector Termination with Program Synthesis

### 2014-07-06 papers/termination/paper.tex
Results table

\newcommand{\xmark}{\ding{55}}
\newcommand{\todo}[1]{{\bf TODO:} #1}
\newcommand{\newC}{C$^-$\xspace}

@@

\begin{figure*}
\centering
\footnotesize
\begin{tabular}{|l|r|c|c|c|c|c|r|r|c|r|r|}
\hline
    & LOC & Terminates? & \shortstack{Linear \\ program?} & \shortstack{Linear ranking \\ function?}  & Conditional? & Float? & Dimension & \shortstack{Ranking \\ program size} & Res & Time (s) & Iterations\\
    \hline
    \hline
\input{table}
    \hline
\end{tabular}

>>>>

\newcommand{\xmark}{\ding{55}}
\newcommand{\tick}{\checkmark}
\newcommand{\todo}[1]{{\bf TODO:} #1}
\newcommand{\newC}{C$^-$\xspace}

@@

\begin{figure*}
\centering
\footnotesize
\begin{tabular}{|l|l||l|r||l|r|r|}
\hline
    &             & \multicolumn{2}{|c||}{\sc ARMC} & \multicolumn{3}{|c|}{\sc Headshot} \\
    & Expected &  Verdict & Time & Verdict & Time & Iterations\\
    \hline
    \hline
\input{table}
    \hline
\end{tabular}
